25 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2018-12-31 manuscript/manuscript.Rmd
last push before furlough

```{r ww_params2, echo=FALSE}
source(here::here("R/functions.R"))
ww_all<-read_csv(here("data/ww_lake_trend_data.csv"))
ww_param_ranges <- ww_all %>%
  filter(param == "chla" |
           param == "temp" |
           param == "total_n" |
           param == "total_p") %>%
  mutate(param = factor(param,levels = c("temp", "total_n", "total_p", "chla"))) %>%
  group_by(param) %>%
  summarize(min = round(min(mn_measurement, na.rm = T), 2),
            percentile_25 = round(quantile(mn_measurement, probs = 0.25, na.rm = T), 2),
            mean = round(mean(mn_measurement, na.rm = T), 2),
            median = round(median(mn_measurement, na.rm = T), 2),
            percentile_75 = round(quantile(mn_measurement, probs = 0.75, na.rm = T), 2),
            max = round(max(mn_measurement, na.rm = T), 2),
            sd = round(sd(mn_measurement, na.rm = T), 2)) %>%
  ungroup() %>%
  mutate(units = c("celsius", "µg/l", "µg/l","µg/l")) %>%
  select(Parameter = param, Units = units, 
         "25th Percentile" = percentile_25,
         Mean = mean, Median = median, 
         "75th Percentile" = percentile_75,
         Max = max, "Std. Dev" = sd )
knitr::kable(ww_param_ranges)
```

```{r setup, include=FALSE}
library(knitr)
library(captioner)
source(here::here("R/functions.R"))
opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
```

```{r analysis, include=FALSE}
#got to figure out path stuff before render.
source(here::here("R/data_available.R")) 
source(here::here("R/summary_stats.R"))  
source(here::here("R/figures.R"))
```

@@

*`r tab_num("ww_params")`*
```{r ww_params, echo=FALSE, results="asis"}
knitr::kable(ww_param_ranges, format = "markdown")
```

@@

*`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.")`*
![](../figures/ww_temp_trends.jpg)

*`r fig_num(name = "tn_ri", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in Rhode Island lakes and ponds.")`*
![](../figures/ww_tn_trends.jpg)

*`r fig_num(name = "tp_ri", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in Rhode Island lakes and ponds.")`*
![](../figures/ww_tp_trends.jpg)

*`r fig_num(name = "chla_ri", caption = "Yearly trend over 20+ years of Chlorphyll *a* (average z-score) in Rhode Island lakes and ponds.")`*
![](../figures/ww_chla_trends.jpg)

@@

*`r fig_num(name = "tn_lagos", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in the LAGOSNE states.")`*
![](../figures/lagos_tn_trends.jpg)

*`r fig_num(name = "tp_lagos", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in the LAGOSNE states.")`*
![](../figures/lagos_tp_trends.jpg)

*`r fig_num(name = "chla_lagos", caption = "Yearly trend over 20+ years of Chlorophyll *a* (average z-score) in the LAGOSNE states.")`*
![](../figures/lagos_chla_trends.jpg)

>>>>

```{r setup, include=FALSE}
library(knitr)
library(captioner)
source(here::here("R/functions.R"), encoding = "UTF-8")
opts_chunk$set(echo = TRUE, fig.width=6, fig.height=5)
tab_num <- captioner(prefix = "Table")
fig_num <- captioner(prefix = "Figure")
```

```{r analysis, include=FALSE}
#got to figure out path stuff before render.
source(here::here("R/data_available.R"), encoding = "UTF-8") 
source(here::here("R/summary_stats.R"), encoding = "UTF-8")  
source(here::here("R/figures.R"), encoding = "UTF-8")
```

@@

```{r ww_params, echo=FALSE, results="asis"}
knitr::kable(ww_param_ranges, format = "markdown")
```

@@

*`r fig_num(name = "temp_ri", caption = "Yearly trend over 20+ years of lake temperature in Rhode Island lakes and ponds.")`*

![](../figures/ww_temp_trends.jpg)

*`r fig_num(name = "tn_ri", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in Rhode Island lakes and ponds.")`*

![](../figures/ww_tn_trends.jpg)

*`r fig_num(name = "tp_ri", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in Rhode Island lakes and ponds.")`*

![](../figures/ww_tp_trends.jpg)

*`r fig_num(name = "chla_ri", caption = "Yearly trend over 20+ years of Chlorphyll *a* (average z-score) in Rhode Island lakes and ponds.")`*

![](../figures/ww_chla_trends.jpg)

@@

*`r fig_num(name = "tn_lagos", caption = "Yearly trend over 20+ years of Total Nitrogen (average z-score) in the LAGOSNE states.")`*

![](../figures/lagos_tn_trends.jpg)

*`r fig_num(name = "tp_lagos", caption = "Yearly trend over 20+ years of Total Phosphorus (average z-score) in the LAGOSNE states.")`*

![](../figures/lagos_tp_trends.jpg)

*`r fig_num(name = "chla_lagos", caption = "Yearly trend over 20+ years of Chlorophyll *a* (average z-score) in the LAGOSNE states.")`*

![](../figures/lagos_chla_trends.jpg)
